Grape Quality and its Link to Regional Differences in the Australian Winegrowing Industry

### 2023-08-07 article.tex
added draft qustions
initial commit toget references to work.

The Australian wine-growing industry is a rich and diverse landscape that is separated into multiple regions that help to describe the unique varietals and qualities that are produced there. While a great deal has been done regarding regional properties and traits, there has been little statistical insight into how regions differ due to a lack of cross-regional and in-depth data sources (Keith Jones, 2002; Knight et al., 2019). In this study we use Classification Trees to compare regional differences and how they relate to sustainable practices and grape quality.
The site of a vineyard predetermines several physical parameters such as climate, geology and soil, making location a widely considered key determinant of grape quality \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,fragaMultivariateClusteringViticultural2017}. This analysis addresses the knowledge gap regarding the effectiveness of regional level strategies employed in the wine industry and their relation to grape quality. Through the use of classification trees this study aims to highlight the key differences in sustainable practices at a regional level and how these practices relate to the different grades of grape quality.

>>>>

% You obviously have no leading question for this paper, and although you do a good job at creating accurate models; it is more important that the research is asking a good question. A cool question as Kate puts it.
%
% The questions I put forward to you are:
%
%   How do winegrowing regions differ?
%   Why is a region different?
%   How do regional differences affect winegrowing?
%   What differences are important between winegrowing regions?
%   
%

The Australian wine-growing industry is a rich and diverse landscape that is separated into multiple regions describing the unique varietals and qualities of wine produced there. While a great deal has been done regarding regional properties and traits, there has been little statistical insight into how regions differ; this has been due to a lack of cross-regional and in-depth data sources   (Keith Jones, 2002; Knight et al., 2019). In this study we use Classification Trees to compare regional differences and how they relate to sustainable practices and grape quality.
The site of a vineyard predetermines several physical parameters such as climate, geology and soil, making location a widely considered key determinant of grape quality \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,fragaMultivariateClusteringViticultural2017}. This analysis addresses the knowledge gap regarding the effectiveness of regional level strategies employed in the wine industry and their relation to grape quality. Through the use of classification trees this study aims to highlight the key differences in sustainable practices at a regional level and how these practices relate to the different grades of grape quality.
